### 2013-07-16 Tex/chapters/conclusion.tex
kurze conclusion

In this thesis the properties of the disordered Ising ferromagnet on two
proximity graphs was studied. This model is within the universality of
the standard Ising ferromagnet. Further the critical temperature depends
on the one hand on the

>>>>

In this thesis the properties of the disordered Ising ferromagnet on two
proximity graphs was studied. This model is within the universality of
the standard Ising ferromagnet. Its critical temperature decreases with
increasing disorder on a RNG. On a GG it first jumps, increases up to
a maximum and decreases after that. The course of the critical
temperatures can be made plausible observing the degree of the underlying
graph, but no explicit formular was found.
